---
title: "pf_soc_med_BC_US_code"
author: "Andy Cox"
date: "6 September 2016"
output: html_document
---


knitr::opts_chunk$set(echo = TRUE)

## R Code  Social Media Data Mining of US Breast Cancer Posts
###Population HER2-  HR+  Advanced or Metastatic  (Stage iv)

First we select the target population from the overall BC posts, the US site breastcancer.org is used as it allows easy identification of the target population from the footnote details supplied by most board users

```{r}
###########################################
#Search and extract posts wiht a term######
###########################################

rm(list = ls())

setwd("/Users/AndyC/Dropbox/rdata/SMposts/BreastCancer_US/results")#3.5GB   1,045,114 posts

#5.563 GB of data     2,534,028 Posts
fls1<-dir()
for(f in fls1){
  dat1<-read.delim(file=f,header=T,sep=",",)
  dat1<-dat1[,-1]
  if(f==fls1[1]){
    #Create data frame to hold posts containing the keywords
    dat2<-dat3<-data.frame(matrix("",0,ncol(dat1)))
    colnames(dat2)<-colnames(dat1)
    colnames(dat3)<-colnames(dat1) 
  }
  
  field1<-as.character(dat1$info_block)#XXXXXXXXXXXXXX
  sel1<-grep("stage iv",field1,ignore.case=T, perl = FALSE, value = FALSE,
             fixed = FALSE)

  dat2<-rbind(dat2,dat1[sel1,])
}

field1<-as.character(dat2$info_block)#XXXXXXXXXXXXXX
sel1<-grep(" her2-",field1,ignore.case=T, perl = FALSE, value = FALSE,
           fixed = FALSE)
dat3<-dat2[sel1,]
dim(dat3)

field1<-as.character(dat3$info_block)#XXXXXXXXXXXXXX
sel1a<-grep(" hr+",field1,ignore.case=T, perl = FALSE, value = FALSE,
           fixed = FALSE)
length(sel1a)

field1<-as.character(dat3$info_block)#XXXXXXXXXXXXXX
sel1b<-grep(" er+",field1,ignore.case=T, perl = FALSE, value = FALSE,
           fixed = FALSE)
length(sel1b)

field1<-as.character(dat3$info_block)#XXXXXXXXXXXXXX
sel1c<-grep(" pr+",field1,ignore.case=T, perl = FALSE, value = FALSE,
           fixed = FALSE)
length(sel1c)           
           
dat4<-dat3[c(sel1a,sel1b,sel1c),]
dim(dat4)

dat44<-dat4
for(i in 1:nrow(dat4))dat44$post[i]<-as.character(unlist(strsplit(dat4$post[i],"wrote: ",fixed=F))[2])

dat_pos


head(dat4$info_block,100)
setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er")
write.table(dat4, file = "BCher_hr.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")
```
Open the file containing posts from the target population only, supressing conversion to factors
At this point the text was transfered to notepad++ and using the search and replace function non ASCI characters were removed manually
```{r}
options(stringsASFactors=FALSE)
setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er")
dat4<-read.delim(file="BCher_hr2.txt",header=T,sep=",",as.is=TRUE)
#Some decriptives
nrow(dat4)
length(unique(dat4$username))
summary(as.numeric(table(dat4$username)))
#Remove frist common part of post wiht date
for(i in 1:nrow(dat4))dat4$post[i]<-as.character(unlist(strsplit(dat4$post[i],"wrote: ",fixed=F))[2])
#Need to emove duplicates
dat4<-dat4[!(duplicated(dat4$post)),]
dat4<-dat4[(nchar(dat4$post)>15),]
write.table(dat4, file = "post_dedup_remmultiB.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")
#This file is the sub population of interest wiht non UTF-* characters removed in the posts section
```

43,521 posts from 1,100 users wiht a median of 8 posts each and a mead of 185.6 posts per user. Minimum of 1 post and maximum of 18,050 posts.
Apparently with a total of 24,164,963,441 views

Clean and remove stopwords and create word frequency table

```{r}
library(tm)
library(slam)

options(stringsASFactors=FALSE)
setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er")
dat5<-read.delim(file="/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/posts_final/post_dedup_remmultiB.csv",header=T,sep=",",as.is=TRUE)

wds1<-as.character(dat5$post)
#wds2<-paste(wds1,collapse=" ")

Encoding(wds1) <- "UTF-8"
iconv(wds1, "UTF-8", "UTF-8",sub='') 
corp1<-Corpus(VectorSource(wds1))
####################################################
corp1<-tm_map(corp1, content_transformer(function(x) iconv(enc2utf8(x), sub = "byte")))
corp1<- tm_map(corp1, removePunctuation,lazy=TRUE)#remove punctuation
corp1<- tm_map(corp1, tolower,lazy=TRUE)#Change to all lower case
corp1 <- tm_map(corp1, removeNumbers,lazy=TRUE)#Remove numbers
stpwds<-stopwords('english')
#stpwds<-stpwds[!(stpwds%in%c('i'))]
corp1 <- tm_map(corp1, removeWords, stpwds,lazy=TRUE)#remove stop words
#########################################
#AddWds<-c("stopped","stop","due")
#corp.yes <- tm_map(corp.yes, removeWords, rmwds)#remove additional words
#########################################
wd3<-unlist(inspect(corp1))
#Remove single letter words
gsub("\\s[:a-z:]\\s"," ",wd3,ignore.case = T)
#Remove excess whitespaces
wd3<-stripWhitespace(wd3)

#Do some housekeeping
rm(corp1)
rm(wds1)

corp2<-Corpus(VectorSource(wd3))
#Create TDM
get.tdm <- function(doc.vec) {
  doc.corpus <- Corpus(VectorSource(doc.vec))
  control <- list(stopwords=FALSE, removePunctuation=FALSE, removeNumbers=TRUE,
                  minDocFreq=4)
  doc.dtm <- TermDocumentMatrix(doc.corpus, control) 
  return(doc.dtm)
}
corp2.tdm <- get.tdm(wd3)

corp2.matrix <- as.matrix(corp2.tdm)


corp2.counts<-slam::row_sums(corp2.tdm, na.rm = T)

corp2.df <- data.frame(cbind(names(corp2.counts),
                           as.numeric(corp2.counts)), stringsAsFactors=FALSE) 

names(corp2.df) <- c("term","frequency") 
corp2.df$frequency <- as.numeric(corp2.df$frequency)

corp2.df<-corp2.df[order(corp2.df$frequency),]

setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/word_freq_final")
write.table(corp2.df, file = "word_freq_cleaned.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")
#read in the freq table and remove all words with 10 or less mentions



###################################
```
Set a new point to read in and process the word frequency table. Remove 10k most common words and create a new word frequency table, this is likely to contain all the chemotherapies

```{r}
wd_dict_pth<-"/Users/AndyC/Dropbox/rdata/text_analysis_ref/most_common_words/google-10000-english-master/google-10000-english-usa.txt"
options(stringsASFactors=FALSE)
setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/word_freq_final")
dat5<-read.delim(file="word_freq_cleaned.csv",header=T,sep=",",as.is=TRUE)

dat5<-dat5[dat5$frequency>20,]
dat5<-dat5[-nrow(dat5),]

cmn_wds<-read.delim(file=wd_dict_pth,header=T,sep="\t",as.is=TRUE)
cmn_wds<-as.vector(cmn_wds[,1])

#Remove common words US
dat5<-dat5[!(dat5$term%in%cmn_wds),]
#save the remnant
dat5<-dat5[order(dat5$term),]

write.table(dat5, file = "word_freq_non_frequent.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")

```

Location
```{r}
locat1<-unique(dat4[,c("username","location")])
locat1<-locat1[!(is.na(locat1$location)),]


locat<-na.omit(dat4$location)

```
#Analysis of post content after substitutiton of chemotherapies and selctions of posts

```{r}
rm(list = ls())
options(stringsASFactors=FALSE)
setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er")
dat1<-read.delim(file="/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/posts_final/post_dedup_remmultiB.csv",header=T,sep=",",as.is=TRUE)

dict1<-read.delim(file="/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/Dictionary/word_tags_master.csv",header=T,sep=",",as.is=TRUE)

chemo1<-dict1$term[dict1$study_specific=="chemotherapy"]
drugs1<-dict1$term[dict1$study_specific=="bc"]

for(p in 1:nrow(dat1)){
  for(w in 1:length(chemo1)){
dat1$post[p]<-gsub(chemo1[w],"chemotherapy",dat1$post[p],ignore.case = T)
}}

for(p in 1:nrow(dat1)){
  for(w in 1:length(drugs1)){
dat1$post[p]<-gsub(drugs1[w],"chemo_flag99",dat1$post[p],ignore.case = T)
  }}

setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/posts_final")

write.table(dat1, file = "t_dedup_remmultiB_chemoReplace.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")

#Select only those that contain teh keywords
sel1<-grep("chemotherapy",dat1$post,ignore.case=T)
sel2<-grep("chemo_flag99",dat1$post,ignore.case=T)

sel3<-unique(c(sel1,sel2))

dat2<-dat1[sel3,]

write.table(dat2, file = "only_chemo.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")
```
#Now move on with word and term frequencies

```{r}
dat2<-read.delim(file="/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/posts_final/only_chemo.csv",header=T,sep=",",as.is=TRUE)

wds1<-as.character(dat2$post)
#wds2<-paste(wds1,collapse=" ")

Encoding(wds1) <- "UTF-8"
iconv(wds1, "UTF-8", "UTF-8",sub='') 
corp1<-Corpus(VectorSource(wds1))
####################################################
corp1<-tm_map(corp1, content_transformer(function(x) iconv(enc2utf8(x), sub = "byte")))
corp1<- tm_map(corp1, removePunctuation,lazy=TRUE)#remove punctuation
corp1<- tm_map(corp1, tolower,lazy=TRUE)#Change to all lower case
corp1 <- tm_map(corp1, removeNumbers,lazy=TRUE)#Remove numbers
stpwds<-stopwords('english')
#stpwds<-stpwds[!(stpwds%in%c('i'))]
corp1 <- tm_map(corp1, removeWords, stpwds,lazy=TRUE)#remove stop words
#########################################
#AddWds<-c("stopped","stop","due")
#corp.yes <- tm_map(corp.yes, removeWords, rmwds)#remove additional words
#########################################
wd3<-unlist(inspect(corp1))
#Remove single letter words
gsub("\\s[:a-z:]\\s"," ",wd3,ignore.case = T)
#Remove excess whitespaces
wd3<-stripWhitespace(wd3)

#Do some housekeeping
rm(corp1)
rm(wds1)

corp2<-Corpus(VectorSource(wd3))
#Create TDM
get.tdm <- function(doc.vec) {
  doc.corpus <- Corpus(VectorSource(doc.vec))
  control <- list(stopwords=FALSE, removePunctuation=FALSE, removeNumbers=TRUE,
                  minDocFreq=4)
  doc.dtm <- TermDocumentMatrix(doc.corpus, control) 
  return(doc.dtm)
}
corp2.tdm <- get.tdm(wd3)

corp2.matrix <- as.matrix(corp2.tdm)


corp2.counts<-slam::row_sums(corp2.tdm, na.rm = T)

corp2.df <- data.frame(cbind(names(corp2.counts),
                           as.numeric(corp2.counts)), stringsAsFactors=FALSE) 

names(corp2.df) <- c("term","frequency") 
corp2.df$frequency <- as.numeric(corp2.df$frequency)

corp2.df<-corp2.df[order(corp2.df$frequency),]

setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/word_freq_final")
write.table(corp2.df, file = "word_freq_target_cleaned.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")

setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/cleaned_posts")
write.table(wd3, file = "posts_target_cleaned.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")
#read in the freq table and remove all words with 10 or less mentions


#Now N grams

#############################
# BI / Trigrams
require(RWeka)
dat2<-read.delim(file="/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/posts_final/only_chemo.csv",header=T,sep=",",as.is=TRUE)

TrigramTokenizer <- function(x) NGramTokenizer(x, Weka_control(min = 2, max = 3))
tdm <- TermDocumentMatrix(wd3, control = list(tokenize = TrigramTokenizer))
tdm <- removeSparseTerms(tdm, 0.95)
inspect(tdm[1:5,1:5])
###############################
m <- as.matrix(tdm)
x<-rowSums(m)
 names(x)<-rownames(m)
 
findFreqTerms(tdm, lowfreq=5)#,highfreq=26)

################################################
mydata.df <- as.data.frame(inspect(tdm))
 mydata.df<-t(mydata.df)
# inspect dimensions of the data frame
nrow(mydata.df)
ncol(mydata.df)
colnames(mydata.df)<-1:ncol(mydata.df)

#Now the data frame (a standard data structure in R) contains a bag of words (specifically, 1-grams) which are simple frequency counts.
 #Though the structure is lost, it retains much information and is simple to use.
 #The data frame is ready for cluster analysis using a cluster analysis function available in R core.
 #The following code is basically copied from Robert I. Kabacof’s “Cluster Analysis” page.
}

#Analysis of topics from thread titles
#The code below takes all thread titles counts frequency of posts within each and lists as a table 

```{r}
options(stringsASFactors=FALSE)

dat6<-read.delim(file="/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/posts_final/only_chemo.csv",header=T,sep=",",as.is=TRUE)
topics1<-substring(dat6$thread,1,100)

cnts<-table(topics1)

topics2<-data.frame(matrix("",length(cnts),2))
colnames(topics2)<-c("topic","count")
topics2[,1]<-names(cnts)
topics2[,2]<-as.numeric(cnts)
topics2<-topics2[order(topics2$count,decreasing=T),]
topics2$views<-0
#Create the views column
for(j in 1:nrow(topics2))
 topics2$views[j]<- dat6$views_n[dat6$thread==topics2$topic[j]][1]

topics2$date<-0
topics2$date_diff<-0
topics2$view_rate<-0
topics2$post_rate<-0
#Standardise the 
#Create the date column
#dat6$date_posted<- gsub("\\s+"," ",dat6$date_posted)
dat6$date_posted<-gsub("(^[[:space:]]+|[[:space:]]+$)", "", dat6$date_posted)
for(j in 1:nrow(topics2)){
 temp<- sort(substr(dat6$date_posted[dat6$thread==topics2$topic[j]],1,12))
temp<-gsub(",","",temp)

topics2$date[j]<- sort(as.Date(temp,format = "%B %d %Y"),descending=F)[1]
topics2$date_diff[j] <- as.numeric(as.Date("2016-09-13")-topics2$date[j])
}
topics2$view_rate<-as.numeric(topics2$views)/as.numeric(topics2$date_diff)
topics2$post_rate<-as.numeric(topics2$count)/as.numeric(topics2$date_diff)

topics2<-topics2[order(topics2$view_rate,decreasing=T),]


#remove the 'Topic:' part formt he thread titles
for(i in 1:nrow(topics2))topics2$topic[i]<-as.character(unlist(strsplit(topics2$topic[i],"Topic: ",fixed=F))[2])

setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/thread_title_final")
write.table(topics2, file = "freq_thread_titles_target.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")
```

dat6$post[grep("Facing the Future",dat6$thread,ignore.case=T)]

dt1$post[grep("Radiation and pain",dt1$thread,ignore.case=T)]




dat_rand<-dat6$post[sample(1:nrow(dat6),nrow(dat6))]

setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/randomized_posts")


write.table(dat_rand,file = "randomized_target_posts.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")

```
#Analysis of drug classes wiht side effects after standardisation of words and terms

```{r}
rm(list = ls())
options(stringsASFactors=FALSE)
dat6<-read.delim(file="/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/posts_final/only_chemo.csv",header=T,sep=",",as.is=TRUE)

#grab only the posts
dat6p<-as.character(dat6$post)
#Load dictionaries

dict_drugnames<-read.delim(file="/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/Dictionary/BC_druganmes_dict.csv",header=T,sep=",",as.is=TRUE)

dict_se<-read.delim(file="/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er/Dictionary/side_effects_dict.csv",header=T,sep=",",as.is=TRUE)

#replace all drugnames wiht higher level class label
patterns1<-as.character(dict_drugnames$term)
repl1<-as.character(dict_drugnames$class_flag)

for(trm in 1:length(patterns1))dat6p<-gsub(patterns1[trm],paste0(" ",repl1[trm]," "),dat6p,ignore.case=T)


#Replace all SE with standardised label
patterns2<-as.character(dict_se$SE)
repl2<-as.character(dict_se$class)

for(trm in 1:length(patterns2))dat6p<-gsub(patterns2[trm],paste0(" ",repl2[trm]," "),dat6p,ignore.case=T)


keepwords<-c(unique(repl1),unique(repl2))

keep_words <- function(text, keep) {
  words <- strsplit(text, " ")[[1]]
  txt <- paste(words[words %in% keep], collapse = " ")
  return(txt)
}

dat7p<-dat6p
for(p in 1:length(dat6p))dat7p[p]<-keep_words(dat6p[p],keepwords)

setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er")
write.table(dat7p,file = "JustFlagTerms_posts.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")


#Create documewnt term matrix
library(tm)
library(slam)


wds1<-as.character(dat7p)
#Remove excess whitespaces
wds1<-stripWhitespace(wds1)


Encoding(wds1) <- "UTF-8"
iconv(wds1, "UTF-8", "UTF-8",sub='') 
corp1<-Corpus(VectorSource(wds1))
####################################################
corp1<-tm_map(corp1, content_transformer(function(x) iconv(enc2utf8(x), sub = "byte")))
#Create TDM
get.tdm <- function(doc.vec) {
  doc.corpus <- Corpus(VectorSource(doc.vec))
  control <- list(stopwords=FALSE, removePunctuation=FALSE, removeNumbers=FALSE,
                  minDocFreq=4)
  doc.dtm <- TermDocumentMatrix(doc.corpus, control) 
  return(doc.dtm)
}
corp2.tdm <- get.tdm(wds1)

corp2.matrix <- as.matrix(corp2.tdm)

library(igraph)


corp2.tdm <- if (inherits(corp2.tdm , "TermDocumentMatrix")) t(corp2.tdm ) else corp2.tdm 
corp2.dtm  <- as.matrix(corp2.tdm )
c <- cor(corp2.dtm)

setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er")
write.table(c,file = "term_correlations.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")

#create correation matrix with only drug classes in columns and SE flags in rows

c1<-c[grep("_flag99",rownames(c)),]
c1<-c1[,grep("_flag11",colnames(c1))]

write.table(c1,file = "term_correlations_filtered.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")

c2<-c1
c2[c2<0]<-0

write.table(c2,file = "term_correlations_filtered_pos.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")
```
