---
title: "pf_soc_med_BC_US_code"
author: "Andy Cox"
date: "6 September 2016"
output: html_document
---


knitr::opts_chunk$set(echo = TRUE)

## R Code  Social Media Data Mining of US Breast Cancer Posts
###Population HER2-  HR+  Advanced or Metastatic  (Stage iv)

First we select the target population from the overall BC posts, the US site breastcancer.org is used as it allows easy identification of the target population from the footnote details supplied by most board users

```{r}
###########################################
#Search and extract posts wiht a term######
###########################################

rm(list = ls())

setwd("/Users/AndyC/Dropbox/rdata/SMposts/BreastCancer_US/results")#3.5GB   1,045,114 posts

#5.563 GB of data     2,534,028 Posts
fls1<-dir()
for(f in fls1){
  dat1<-read.delim(file=f,header=T,sep=",",)
  dat1<-dat1[,-1]
  if(f==fls1[1]){
    #Create data frame to hold posts containing the keywords
    dat2<-dat3<-data.frame(matrix("",0,ncol(dat1)))
    colnames(dat2)<-colnames(dat1)
    colnames(dat3)<-colnames(dat1) 
  }
  
  field1<-as.character(dat1$info_block)#XXXXXXXXXXXXXX
  sel1<-grep("stage iv",field1,ignore.case=T, perl = FALSE, value = FALSE,
             fixed = FALSE)

  dat2<-rbind(dat2,dat1[sel1,])
}

field1<-as.character(dat2$info_block)#XXXXXXXXXXXXXX
sel1<-grep(" her2-",field1,ignore.case=T, perl = FALSE, value = FALSE,
           fixed = FALSE)
dat3<-dat2[sel1,]
dim(dat3)

field1<-as.character(dat3$info_block)#XXXXXXXXXXXXXX
sel1a<-grep(" hr+",field1,ignore.case=T, perl = FALSE, value = FALSE,
           fixed = FALSE)
length(sel1a)

field1<-as.character(dat3$info_block)#XXXXXXXXXXXXXX
sel1b<-grep(" er+",field1,ignore.case=T, perl = FALSE, value = FALSE,
           fixed = FALSE)
length(sel1b)

field1<-as.character(dat3$info_block)#XXXXXXXXXXXXXX
sel1c<-grep(" pr+",field1,ignore.case=T, perl = FALSE, value = FALSE,
           fixed = FALSE)
length(sel1c)           
           
dat4<-dat3[c(sel1a,sel1b,sel1c),]
dim(dat4)

head(dat4$info_block,100)
setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er")
write.table(dat4, file = "BCher_hr.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")
```
Open the file containing posts from the target population only, supressing conversion to factors

```{r}
options(stringsASFactors=FALSE)
setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er")
dat4<-read.delim(file="BCher_hr2.txt",header=T,sep=",",as.is=TRUE)
#Some decriptives
nrow(dat4)
length(unique(dat4$username))
summary(as.numeric(table(dat4$username)))
```

214,896 posts from 1,156 users wiht a median of 8 posts each and a mead of 185.6 posts per user. Minimum of 1 post and maximum of 18,050 posts.
Apparently with a total of 24,164,963,441 views

```{r}
library(tm)
library(slam)
wd_dict_pth<-"/Users/AndyC/Dropbox/rdata/text_analysis_ref/most_common_words/google-10000-english-master/google-10000-english-usa.txt"

wds1<-as.character(dat4$post)

#wds2<-paste(wds1,collapse=" ")


findOffendingCharacter <- function(x, maxStringLength=10000){  
  print(x)
  for (c in 1:maxStringLength){
    offendingChar <- substr(x,c,c)
    #print(offendingChar) #uncomment if you want the indiv characters printed
    #the next character is the offending multibyte Character
  }    
}

lapply(wds1, findOffendingCharacter)

wds2<-wds1[21170:length(wds1)]




 






  #replace the \n notations
wds2<-gsub("\n",replacement=" ",x=wds1)
wds2<-gsub("\t",replacement=" ",x=wds2)
wds2<-gsub("/",replacement=" ",x=wds2)


#remove leading and trailing white spaces
wds2<-gsub("^\\s+|\\s+$", "", wds2)
#####################Deal wiht non UTF

Encoding(wds1) <- "UTF-8"
iconv(wds1, "UTF-8", "UTF-8",sub='') 

corp1<-Corpus(VectorSource(wds1))
####################################################
corp1<-tm_map(corp1, content_transformer(function(x) iconv(enc2utf8(x), sub = "byte")))



corp1<- tm_map(corp1, removePunctuation,lazy=TRUE)#remove punctuation
corp1<- tm_map(corp1, tolower,lazy=TRUE)#Change to all lower case
corp1 <- tm_map(corp1, removeNumbers,lazy=TRUE)#Remove numbers
stpwds<-stopwords('english')
#stpwds<-stpwds[!(stpwds%in%c('i'))]
corp1 <- tm_map(corp1, removeWords, stpwds,lazy=TRUE)#remove stop words
#########################################
#AddWds<-c("stopped","stop","due")
#corp.yes <- tm_map(corp.yes, removeWords, rmwds)#remove additional words
#########################################
wd3<-unlist(inspect(corp1))
#Remove single letter words
gsub("\\s[:a-z:]\\s"," ",wd3,ignore.case = T)
#Remove excess whitespaces
wd3<-stripWhitespace(wd3)

#Do some housekeeping
rm(corp1)
rm(wds1)

corp2<-Corpus(VectorSource(wd3))
#Create TDM
get.tdm <- function(doc.vec) {
  doc.corpus <- Corpus(VectorSource(doc.vec))
  control <- list(stopwords=FALSE, removePunctuation=FALSE, removeNumbers=TRUE,
                  minDocFreq=4)
  doc.dtm <- TermDocumentMatrix(doc.corpus, control) 
  return(doc.dtm)
}
corp2.tdm <- get.tdm(wd3)

corp2.matrix <- as.matrix(corp2.tdm)


corp2.counts<-slam::row_sums(corp2.tdm, na.rm = T)

corp2.df <- data.frame(cbind(names(corp2.counts),
                           as.numeric(corp2.counts)), stringsAsFactors=FALSE) 

names(corp2.df) <- c("term","frequency") 
corp2.df$frequency <- as.numeric(corp2.df$frequency)

corp2.df<-corp2.df[order(corp2.df$frequency),]

setwd("/Users/AndyC/Dropbox/rdata/pfizerSocMedBC/data/BC_stg5_her2_er")
write.table(corp2.df, file = "word_freq_cleaned.csv", sep = ",", col.names = NA, na="NA", qmethod = "double")
#read in the freq table and remove all words with 10 or less mentions



###################################
```


